---
title: "AS03_join_edu_data"
author: "龔泓愷"
date: "10/10/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: no
    theme: cerulean
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE, warning=FALSE}
library(tidyverse)
options(stringsAsFactors = F)
```

# Q1 Joining educational data
- Reading educational data from the following csv file.

## Town level educational data

- Original data is village-level data
- Following In-Class tutorial, using `group_by()` to create town-level statistical data.

```{r, message=FALSE, warning=FALSE}
edu_town <- read_csv("data/opendata107Y020.csv") %>%
  slice(-1) %>% # 移除中文標題
  mutate_at(vars(contains("edu")), funs(as.numeric(.))) %>% # 把 char 轉 num
  mutate(site_id = str_replace(site_id, "鳳山一", "鳳山區")) %>% 
  mutate(site_id = str_replace(site_id, "鳳山二", "鳳山區")) %>%
  mutate(site_id = str_replace(site_id, "三民一", "三民區")) %>% 
  mutate(site_id = str_replace(site_id, "三民二", "三民區")) %>%
  mutate(site_id = str_replace(site_id, "　", "")) %>% # "北 區" > "北區"
  group_by(site_id) %>%
  summarise_at(vars(contains("edu")), funs(sum)) %>% # 含有 edu 的欄位分別依 group 加總
  glimpse()
```


```{r}
#edu_town_long <- edu_town %>%
#  gather(key = "key", "value", -site_id) %>%
#  mutate(key = str_replace(key, "illiterate", "illiterate_illiterate")) %>%
#  mutate(key = str_replace(key, "selftaughtl", "selftaught_selftaught")) %>%
#  mutate(key = str_replace(key, "juniorcollege_2ys", "juniorcollege2ys")) %>%
#  mutate(key = str_replace(key, "juniorcollege_5ys_final2y", "juniorcollege5ysfinal2y"))  %>%
#  mutate(key = str_replace(key, "juniorcollege_5ys_first3y", "juniorcollege5ysfirst3y"))
```

## Loading town-level age, marriage, and referendum data
- Loading town-level data created in class

```{r message=FALSE, warning=FALSE}
age_town <- read_csv("data/opendata107Y030.csv") %>%
  slice(-1) %>%
  mutate(vname  = paste0(site_id, village)) %>%
  mutate_at(vars(c(contains("_f"), contains("_m"))), funs(as.numeric(.))) %>% # 把 char 轉 num
  mutate(site_id = str_replace(site_id, "鳳山一", "鳳山區")) %>% 
  mutate(site_id = str_replace(site_id, "鳳山二", "鳳山區")) %>%
  mutate(site_id = str_replace(site_id, "三民一", "三民區")) %>% 
  mutate(site_id = str_replace(site_id, "三民二", "三民區")) %>%
  mutate(site_id = str_replace(site_id, "　", "")) %>% # "北 區" > "北區"
  group_by(site_id) %>%
  summarise_at(vars(c(contains("_f"), contains("_m"))), funs(sum)) %>% # 含有 edu 的欄位分別依 group 加總
  glimpse()

town_stat <- readRDS("town_stat.RDS")
  
town_ref10 <- readRDS("town_ref10.rds")
```


## Joining data together
- Joining all town-leave data together (Including new educational dada, and age, marriage, referendum data introduced in class)
```{r message=FALSE, warning=FALSE}
join <- town_ref10 %>%
  inner_join(edu_town, by = c("townfull" = "site_id")) %>%
  inner_join(age_town, by = c("townfull" = "site_id")) %>%
  inner_join(town_stat, by = c("townfull" = "site_id"))
```

## **Q1 Ans: Joined data dimension**
- using `dim()` to display data dimension (should be 368). TAs will score Q1 according to the outcome.
```{r message=FALSE, warning=FALSE}
# dim(YOUR_DATA_FRAME_NAME)

dim(join)
```


## **Q1 Ans: glimpse()**
- Using `glimpse()` to print out data you join below. TAs will score Q1 according to the `glimpse()` outcome.
```{r message=FALSE, warning=FALSE}
# glimpse(YOUR_DATA_FRAME_NAME)

glimpse(join)
```

# Q2 Open Question - Joining one more dimension
- TASK: Collecting one more dimension from open data for town level and join it with the eucation, married, age, and referendum data.

## Read the file
```{r message=FALSE, warning=FALSE}
pop_town <- read_csv("data/opendata106N0101.csv")[,c("site_id", "population_density")]

join_pop <- join %>%
  inner_join(pop_town, by = c("townfull" = "site_id"))
```

## Display the data dimension of the file
```{r}
dim(join_pop)
```

## **Q2 Ans: Answer following questions**
- Data source link (the page you download the data): [Link](https://data.moi.gov.tw/MoiOD/Data/DataDetail.aspx?oid=D1450798-F85B-4063-9761-A24B8929A684)
- Describe the data source in your words: 

> 使用 106 年內政部資料開放平台，各鄉鎮市區人口密度

## **Q2 Ans: Dim() of joined data frame**

```{r}
# dim(YOUR_DATA_FRAME_NAME)

dim(join_pop)
```


## **Q2 Ans: glimpse() of joined data frame**
```{r}
# glimpse(YOUR_DATA_FRAME_NAME) 

glimpse(join_pop)
```

# Q3 Open question - Linear regression
 - Now, you have age, marriage, and education as indenpendent variables and referendum 10th agreement as the dependent variable.
 - Go online and search how to run regression with R
 - Report the regression result 

## **Q3 Ans**
```{r message=FALSE, warning=FALSE}
# Perc_agree vs. Married Perc
mod1 <- lm(formula = perc_agree ~ marriedPerc, data = join_pop)
summary(mod1); cor.test(join_pop$perc_agree, join_pop$marriedPerc)

plt1 <- ggplot(data = join_pop, aes(x = marriedPerc, y = perc_agree)) + 
  geom_point() + 
  geom_abline(intercept = coef(mod1)[1], slope = coef(mod1)[2],  color = "dodgerblue") + 
  theme_minimal()
```

    mod1 線性回歸結果：斜率 = 0.48590, y 截距 = 0.37413
    從 p_value 與結果可以得知該回歸通過 alpha = 0.001 的顯著檢定
    從 R^2 可以得知該回歸僅能解釋約 11% 的變異
    兩者的相關係數為 0.33

```{r message=FALSE, warning=FALSE}
# Perc_agree vs. pop_density
mod2 <- lm(formula = perc_agree ~ population_density, data = join_pop)
summary(mod2); cor.test(join_pop$perc_agree, join_pop$population_density)

plt2 <- ggplot(data = join_pop, aes(x = population_density, y = perc_agree)) + 
  geom_point() + 
  geom_smooth(method = 'lm', se = FALSE, color = "dodgerblue") +
  scale_x_log10() +
  theme_minimal()
```

    mod2 線性回歸結果：斜率 = -3.329e-06, y 截距 = 7.295e-01
    從 p_value 與結果可以得知該回歸通過 alpha = 0.001 的顯著檢定
    從 R^2 可以得知該回歸能解釋約 30% 的變異
    兩者的相關係數為 -0.55
    
```{r message=FALSE, warning=FALSE}
library(gridExtra)

grid.arrange(plt1, plt2, ncol=2)
```
  

# Q4 Challenge: The median of grouped data
- Calculating age median of grouped data
- Reference: https://www.themathdoctors.org/finding-the-median-of-grouped-data/
- Solve it with dplyr pkgs
- If you can't answer the question correctly, keep your code (even wrong) to get partial scores.

## **Q4 Ans: glimpse()**
```{r}
# glimpse(YOUR_DATA_FRAME_NAME)
age_town_tidy <- age_town %>%
  gather(key = "key", "value", -site_id) %>%
  mutate(key = str_replace(key, "15down", "0_14")) %>%
  mutate(key = str_replace(key, "100up", "100_105")) %>%
  mutate(key = str_replace(key, "single_age", "single")) %>%
  separate(key, c("married", "ageLower", "ageUpper", "gender")) %>%
  mutate(ageLower = as.numeric(ageLower),
         ageUpper = as.numeric(ageUpper),
         value = as.numeric(value))

glimpse(age_town_tidy)
  
age_town_group <- age_town_tidy %>%
  group_by(site_id, ageLower) %>%
  summarise(value = sum(value))

# 找出中位數所在區間
index <- function(val) {
  sum = 0
  for (i in 1:length(val)) {
    sum = sum + val[i]
    if (sum >= sum(val)/2) {
      return (i)
      break
    }
  }
}

# 找出 median_group 必要參數並計算
group_median <- function(val, w = 5) {
  ind = index(val)
  L = df$ageLower[ind]
  B = sum(df$value[1:(ind-1)])
  n = sum(val)
  G = df$value[ind]
  
  median = L + ((n/2) - B)/G * w
  return(median)
}

# 對每個行政區套用 median_group
median <- vector()

for (site in age_town$site_id) {
  df <- filter(age_town_group, site_id == site)
  val <- df$value
  tmp <- group_median(val)
  median <- c(median, tmp)
}

result.df = data.frame(site_id = age_town$site_id, median = median)
result.df
```

